
\chapter{Contract DemiurgeStore}

\minitoc

\section{Overview}

In file {\tt DemiurgeStore.sol}

This contract is used to store ``global'' values for the whole
infrastructure, such as the code of the contracts to be deployed and
the addresses of some contracts.

\section{General Minor-level Remarks}

In general, the infrastructure would be safer if this contract would
be implemented in two phases:
\begin{itemize}
\item In the Initialization phase, the contract is waiting for all the
  {\tt setXXX} methods to be called to initialize all the fields. A
  bitmap can be used to keep the current initialization state. Any
  attempt to user a {\tt getXXX} method should fail.
\item In the Post-Initalization phase, the contract accepts to reply
  to {\tt getXXX} methods, but {\tt setXXX} methods are disabled.
\end{itemize}

There is also an inconsistency between the getters and setters:
getters are generic (they take a {\tt kind} as argument), whereas
setters are specific (there is a different one for every kind).

\section{Public Functions}

\subsection{Function queryAddr}

\begin{itemize}
\item Minor issue: a {\tt require} could be added to fail if {\tt
  kind} is not a well-known kind.
\end{itemize}

\begin{lstlisting}[firstnumber=43]
    function queryAddr(ContractAddr kind) public view {
        address addr = _addrs[uint8(kind)];
        IDemiurgeStoreCb(msg.sender).updateAddr{value: 0, flag: 64, bounce: false}(kind, addr);
    }
\end{lstlisting}

\subsection{Function queryCode}

\begin{itemize}
\item Minor issue: a {\tt require} could be added to fail if {\tt
  kind} is not a well-known kind.
\end{itemize}

\begin{lstlisting}[firstnumber=38]
    function queryCode(ContractType kind) public view {
        TvmCell code = _codes[uint8(kind)];
        IDemiurgeStoreCb(msg.sender).updateCode{value: 0, flag: 64, bounce: false}(kind, code);
    }
\end{lstlisting}

\subsection{Function setPadawanCode}

\begin{itemize}
\item Minor issue: the infrastructure would probably be safer if the
  expected code hash is hardcoded in the source code, and check
  through a {\tt require}
\end{itemize}

\begin{lstlisting}[firstnumber=14]
    function setPadawanCode(TvmCell code) public signed {
        _codes[uint8(ContractType.Padawan)] = code;
    }
\end{lstlisting}

\subsection{Function setProposalCode}

\begin{itemize}
\item Minor issue: the infrastructure would probably be safer if the
  expected code hash is hardcoded in the source code, and check
  through a {\tt require}
\end{itemize}

\begin{lstlisting}[firstnumber=17]
    function setProposalCode(TvmCell code) public signed {
        _codes[uint8(ContractType.Proposal)] = code;
    }
\end{lstlisting}
