
\chapter{Contract Group}

\minitoc

\section{Overview}

In file {\tt Group.sol}

\section{Contract Inheritance}

\noindent\begin{tabular}{|l|p{5cm}|}\hline
Base & \\\hline
IGroup & \\\hline
\end{tabular}


\section{Static Variable Definitions}

\begin{lstlisting}[firstnumber=11]
    string static _name;
\end{lstlisting}

\section{Variable Definitions}

\begin{lstlisting}[firstnumber=12]
    address[] _members;
\end{lstlisting}

\section{Constructor Definitions}

\subsection{Constructor}

\begin{itemize}
\item \issueCritical{No permission check in {\tt Group.constructor}}
  {No permission check is performed on the deployer of the contract.
    As a consequence, an attacker could deploy a {\tt Group} contract
    for a given name before the user, if it can predict that the user
    will use that name, and the attacker could initialize the contract
    with his own list of (malicious) members. Fix: add a static
    variable in the contract, with the only allowed deployer of the
    contract and check that the sender is the allowed deployer in the
    constructor. }
\end{itemize}

\begin{lstlisting}[firstnumber=15]
    constructor(address[] initialMembers) public onlyContract {
        _members = initialMembers;
    }
\end{lstlisting}

\section{Public Method Definitions}


\subsection{Function addMember}

\begin{itemize}
\item \issueCritical{No permission check in {\tt Group.addMember}}{An
  attacker could add any member to the group because no permission
  check is performed in this function}
\item Minor issue: a member can be added several times in the
  group. Fix: use a mapping and only add non-existing members.
\item Minor issue: the argument {\tt idProposal} is not used.
\end{itemize}

\begin{lstlisting}[firstnumber=25]
    function addMember(uint128 idProposal, address member) public onlyContract {
        idProposal;
        _members.push(member);
    }
\end{lstlisting}

\subsection{Function getMembers}

\begin{itemize}
\item OK
\end{itemize}

\begin{lstlisting}[firstnumber=19]
    function getMembers() override public onlyContract {
        IGroupCallback(msg.sender).onGetMembers
            {value: 0, flag: 64, bounce: true}
            (_name, _members);
    }
\end{lstlisting}

\subsection{Function removeMember}

\begin{itemize}
\item \issueCritical{No permission check on {\tt removeMember}}{An
  attacker could remove any member of the group, as no permission
  check is performed.}
\item Minor issue: the argument {\tt idProposal} is not used.
\end{itemize}

\begin{lstlisting}[firstnumber=30]
    function removeMember(uint128 idProposal, address member) public onlyContract {
        idProposal;
        address[] members;
        for(uint32 index = 0; index < _members.length; index++) {
            if(_members[index] != member) {
                members.push(_members[index]);
            }
        }
        _members = members;
    }
\end{lstlisting}
